Title

### 2013-03-14 inc/extension/external_forces/formal.tex
include most of the comments through RF cavity practical extension

For the case of a cylindrically symmetric perfect lens, or in the longitudinal direction a perfect RF compression element, with a parabolic potential, the external force is linear with distance from the center of the electron pulse: 
\begin{equation} \label{eq:linear_force}
\vec{F}_{ext} = - M_{ \smallT } r \hat{\operatorname{r}} - M_{z} z \hat{\operatorname{z}} \text{ .}
\end{equation}
Here, $M_{ \smallT }$ and $M_{z}$ characterize the strength of a lens or a compressor, respectively, and are chosen to be positive for focusing/compression elements.
Substitution into the integral equation for the $ K^{ext} $ matrix elements,
\begin{equation}
 \begin{split} 
  K^{ext}_{ij} & \equiv \dfrac{1} {N} \int u_{i} u_{j} ( \vec{\nabla}_{p} f ) \cdot \vec{F}_{ext} d^{3} x d^{3} p \\ & = \dfrac{1} {N} \int u_{i} u_{j} \biggl[ x \left( \dfrac{ p_{x} } { \eta_{ \smallT } } - \dfrac{ \gamma_{ \smallT } x } { \sigma_{ \smallT } \eta_{ \smallT } } \right) + y \left( \dfrac{ p_{y} } { \eta_{ \smallT } } - \dfrac{ \gamma_{ \smallT } y } { \sigma_{ \smallT } \eta_{ \smallT } } \right) \\ & \quad + z \left( \dfrac{ p_{z} } { \eta_{z} } - \dfrac{ \gamma_{z} z } { \sigma_{z} \eta_{z} } \right) \biggr] f d^{3} x d^{3} p ,
 \end{split}
\end{equation}
leads to the $6\times6$ matrix
\begin{equation}
K^{ext} = 
\begin{pmatrix}
\hat{k}^{lin}_{\smallT} & \hat{0} & \hat{0} \\
\hat{0} & \hat{k}^{lin}_{\smallT} & \hat{0} \\
\hat{0} & \hat{0} & \hat{k}^{lin}_{z}
\end{pmatrix} \text{ ,}
\end{equation}
where
\begin{equation}
\hat{k}^{lin}_{\alpha} =
\begin{pmatrix}
0 & M_{\alpha} \sigma_{\alpha} \\
M_{\alpha} \sigma_{\alpha} & 2 M_{\alpha} \gamma_{\alpha} \text{.}
\end{pmatrix} \text{ .}
\end{equation}
which by \ref{eq:dainvdt} yields an additional term $M_{\alpha} \sigma_{\alpha}$ which is added to the original $\dfrac{d \gamma_{\alpha}}{d t}$ equation.
This derivation has been for a single force, in practice however there may be multiple forces.
Therefore if each force is labeled by $f$, \ref{eq:ag_big_gamma_gamma} may be restated as
\begin{equation}
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi) + \sigma_{\alpha} \sum\limits_{f} M_{\alpha}^{\lbrace f \rbrace} 
\end{equation}

>>>>

For the case of a cylindrically symmetric perfect lens, or in the longitudinal direction a perfect RF compression element, with a parabolic potential, the external force is linear with distance from the center of the electron pulse: 
\begin{equation} \label{eq:linear_force}
\vec{F}_{ext} = - M_{ \smallT } r \hat{\operatorname{r}} - M_{z} z \hat{\operatorname{z}} \text{ .}
\end{equation}
Here, $M_{ \smallT }$ and $M_{z}$ characterize the strength of a lens or a compressor, respectively, and are chosen to be positive for focusing/compression elements.
Substitution into the integral equation for the $ K^{ext} $ matrix elements,
\begin{equation}
 \begin{split} 
  K^{ext}_{ij} & \equiv \dfrac{1} {N} \int u_{i} u_{j} ( \vec{\nabla}_{p} f ) \cdot \vec{F}_{ext} d^{3} x d^{3} p \\ & = \dfrac{1} {N} \int u_{i} u_{j} \biggl[ x \left( \dfrac{ p_{x} } { \eta_{ \smallT } } - \dfrac{ \gamma_{ \smallT } x } { \sigma_{ \smallT } \eta_{ \smallT } } \right) + y \left( \dfrac{ p_{y} } { \eta_{ \smallT } } - \dfrac{ \gamma_{ \smallT } y } { \sigma_{ \smallT } \eta_{ \smallT } } \right) \\ & \quad + z \left( \dfrac{ p_{z} } { \eta_{z} } - \dfrac{ \gamma_{z} z } { \sigma_{z} \eta_{z} } \right) \biggr] f d^{3} x d^{3} p ,
 \end{split}
\end{equation}
leads to the $6\times6$ matrix
\begin{equation}
K^{ext} = 
\begin{pmatrix}
\hat{k}^{lin}_{\smallT} & \hat{0} & \hat{0} \\
\hat{0} & \hat{k}^{lin}_{\smallT} & \hat{0} \\
\hat{0} & \hat{0} & \hat{k}^{lin}_{z}
\end{pmatrix} \text{ ,}
\end{equation}
where
\begin{equation}
\hat{k}^{lin}_{\alpha} =
\begin{pmatrix}
0 & M_{\alpha} \sigma_{\alpha} \\
M_{\alpha} \sigma_{\alpha} & 2 M_{\alpha} \gamma_{\alpha} \text{.}
\end{pmatrix} \text{ .}
\end{equation}
which by \ref{eq:dainvdt} this yields an additional term $M_{\alpha} \sigma_{\alpha}$ which is added to the original $\dfrac{d \gamma_{\alpha}}{d t}$ equation.
This derivation has been for a single force, in practice however there may be multiple forces.
Therefore if each force is labeled by $f$, \ref{eq:ag_big_gamma_gamma} may be restated as
\begin{equation}
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi) + \sigma_{\alpha} \sum\limits_{f} M_{\alpha}^{\lbrace f \rbrace} 
\end{equation}

### 2013-03-14 inc/extension/external_forces/practical.tex
fix bug
include most of the comments through RF cavity practical extension

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

Of course, physical electron-optical elements occupy only a finite space in the column, and thus their influence on the pulse should be limited to a region near the element itself.
To localize the mathematical result shown in Section \ref{sec:external_forces}, it is convenient to redefine $M_{i}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{i}	\to M_{i} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{\smallzero} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

A full description of the motion of the electrons is easily derived \cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -e B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = e r \dot{r} B_z - e r B_r \dot{z} \\
  m \ddot{z} = e B_r r \dot{\theta}
\end{gather}
\end{subequations}
however, attempting to further seperate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
The full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell \cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$ in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q }
\end{gather}
\end{subequations}
%%TODO I can't decide whether the Q and k definitions should be numbered or not
%where
%\begin{gather*}
%  Q \equiv (a+r)^2 + z^2 \\
%  k \equiv \sqrt{ 4 a r / Q }
%\end{gather*}
and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

For localizing the region of influence of the lens, I have commonly modelled a thin magnetic lens as having a super-Gaussian order value $n=1$, a simple Gaussian; of course this may depend on the specifics of the lens.
To simulate the effect of magnetic lenses in a UEM by the extended AG model, for each magnetic lens, add a term like
\begin{equation} \label{eq:reg_of_influence}
  M_{\smallT}^{mag} = M_{\smallT}^{mag}(I) \exp \left [ - \left (  \frac{ z^{\prime} - z_{mag}^{\prime} }{ L_{mag} / 2 } \right )^{ 2 } \right ] \text{ ,}
\end{equation}
to the set of $M_{\smallT}$ parameters, where $z_{mag}^{\prime}$ and $L_{mag}$ are the position and length of the lens in question respectively.
%TODO include discussion and plot of beam size versus aberrations

\ref{fig:mag_lens_loops} shows electron rays tracked kinematically (by employing \ref{eq:lens_eq_of_motion}) through a realistic magnetic lens simulation (shown in green).
The kinematic model employs ten individual current loops generating magnetic fields described by \ref{eq:field_of_loop}; these loops occupy a total length of 635$\mu$m at position $z=0$.
Each ray bunch consists of one ray parallel to the axis of propagation and one each having an inward or outward transverse velocity related to an excess photoemission energy $\Delta E \approx $ 0.1eV.
The bunches are distributed evenly from $r=0$ to $r = 1$mm.
These are compared with an AG model simulation of a Guassian electron beam of HW1/eM beam width $ w = 500 \mu\text{m} $ having an initial transverse variance of the same $\Delta E$.

@@

The spatial dependence of the axial RF electric field experienced by the electron pulse in a TM$_{010}$ cavity of radius $a$ may be written as
\begin{equation} \label{eq:RF_Efield}
  E ( r , z , z^{\prime} ) = E_{0} \sin \left ( \frac{ \Omega ( z^{\prime} - z ) }{ v_{\smallzero} } + \phi \right )\operatorname{J_{0}} \left ( \frac{ k r }{ a } \right ) \text{,}
\end{equation}
where $ E_{ 0 } $ is the oscillating field amplitude, $\Omega$ is the RF frequency and $\phi$ is a phase factor determining whether the RF cavity acts as a pulse compressor $ ( \phi \approx 0 ) $ or an electron accelerator $ ( \phi \approx \pm \pi/2 ) $.
The coordinate $z^{\prime} $ describes the position of the center of the pulse in the RF cavity, which extends from $ z^{\prime} = - d / 2 $ to $ z^{\prime} = d / 2 $, and $z$ is the position of any electron in the pulse with respect to the center of the pulse.
For the $\text{TM}_{010}$ oscillation mode, the RF frequency is given by
\begin{equation}
  \Omega = \frac{ c k }{a} \text{,}
\end{equation}
where $c$ is the speed of light in a vacuum and $ k = 2.405 $ is the first zero of the $\operatorname{ J_{0} }$ Bessel function.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs \cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

To summarize, the additional terms are which are added to model the internal pulse dynamics arising from a single RF cavity are
\begin{gather}
  M_{z}^{RF} = \left [ \frac{ e \Omega E_{0} }{ v_{\smallzero} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \\
  \begin{aligned}
  M_{\smallT}^{RF} = & e E_{0} \left [ \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \right. \\ \times & \left. \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ]
  \end{aligned}
\end{gather}
Additionally, since an RF cavity can act as a pulse accelerator (as seen in the leading term of \ref{eq:RF_Efield_approx}) an additional force term
\begin{equation}
  F_{z}^{RF} = E_{0} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \, \text{,}
\end{equation}
should be added to the equation of motion governing the propagation of the pulse down the column.
% excluded example section from JAP paper as it will need new graphics

>>>>

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section, I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

%TODO perhaps this shouldn't be a redefinition, but some other function
Of course, physical electron-optical elements occupy only a finite space in the column, and thus their influence on the pulse should be limited to a region near the element itself.
To localize the mathematical result shown in Section \ref{sec:external_forces}, it is convenient to redefine a particular $M_{\alpha}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{\alpha} \to M_{\alpha} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the axial length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{\smallzero} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

The full description of the motion of an electron (in cylindrical coordinates $r, \theta, z$) in an azimuthally symmetric magnetic field ($\vec{B} = B_r \hat{r} + B_z \hat{z}$) is easily derived \cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -q B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = q r \dot{r} B_z - q r B_r \dot{z} \\
  m \ddot{z} = q B_r r \dot{\theta}
\end{gather}
\end{subequations}
where each dot denotes a time derivative.
Attempting to further seperate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
Compounding the problem, the full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell \cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$, again in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  \frac{B_z}{\mu} = H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  \frac{B_r}{\mu} = H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q }
\end{gather}
\end{subequations}
%%TODO I can't decide whether the Q and k definitions should be numbered or not
%where
%\begin{gather*}
%  Q \equiv (a+r)^2 + z^2 \\
%  k \equiv \sqrt{ 4 a r / Q }
%\end{gather*}
where $\mu$ is the local magnetic permability, $H$ is the auxiliary field, and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
In the vacuum, $\mu$ is simply the usual free space permeability $\mu_0$; in Section \ref{sec:mag_lens}, we will see how this permeability can be used to improve the performance of magnetic lenses.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

For localizing the region of influence of the lens, I have generally modelled a thin magnetic lens as having a super-Gaussian order value $n=1$, a simple Gaussian; of course this may depend on the specifics of the lens.
To simulate the effect of magnetic lenses in a UEM by the extended AG model, for each magnetic lens, one adds a term like
\begin{equation}
  M_{\smallT}^{mag} = M_{\smallT}^{mag}(I) \exp \left [ - \left (  \frac{ z^{\prime} - z_{mag}^{\prime} }{ L_{mag} / 2 } \right )^{ 2 } \right ] \text{ ,}
\end{equation}
to the set of $M_{\smallT}$ parameters, where $z_{mag}^{\prime}$ and $L_{mag}$ are the position and length of the lens in question respectively.
%TODO include discussion and plot of beam size versus aberrations

\ref{fig:mag_lens_loops} shows electron rays tracked kinematically (by employing \ref{eq:lens_eq_of_motion}) through a realistic magnetic lens simulation (shown in green).
The kinematic model employs ten individual current loops generating magnetic fields described by \ref{eq:field_of_loop}; these loops occupy a total length of 635$\mu$m at position $z=0$.
These loops each carry a current of 45A; this approximates a more realistic stack of 10 loops carrying 4.5A, thus simulating a  100 turn solenoid in a 10x10 array.
Each ray bunch consists of one ray parallel to the axis of propagation and one each having a longitudinal velocity of $1 \times 10^{8}$ m/s and an inward or outward transverse velocity related to an excess photoemission energy $\Delta E \approx $ 0.1eV.
The bunches are distributed evenly from $r=0$ to $r = 1$mm.
These are compared with an AG model simulation of a Guassian electron beam of HW1/eM beam width $ w = 500 \mu\text{m} $ having an initial transverse momentum variance associated with $\Delta E$.

@@

The spatial dependence of the axial RF electric field experienced by the electron pulse in a TM$_{010}$ cavity of radius $a$ may be written as
\begin{equation} \label{eq:RF_Efield}
  E ( r , z , z^{\prime} ) = E_{0} \sin \left ( \frac{ \Omega ( z^{\prime} - z ) }{ v_{\smallzero} } + \phi \right )\operatorname{J_{0}} \left ( \frac{ k r }{ a } \right ) \text{,}
\end{equation}
where $ E_{ 0 } $ is the oscillating field amplitude, $\Omega$ is the RF frequency and $\phi$ is a phase factor determining whether the RF cavity acts as a pulse compressor $ ( \phi \approx 0 ) $ or an electron accelerator $ ( \phi \approx \pm \pi/2 ) $.
The coordinate $z^{\prime} $ describes the position of the center of the pulse in the RF cavity, which extends from $ z^{\prime} = - d / 2 $ to $ z^{\prime} = d / 2 $, and $z$ is the position of any electron in the pulse with respect to the center of the pulse.
For the $\text{TM}_{010}$ oscillation mode, the RF frequency is given by
\begin{equation}
  \Omega = 2.405 \frac{ c }{a} \text{,}
\end{equation}
where $c$ is the speed of light in a vacuum and 2.405 is the first zero of the $\operatorname{ J_{0} }$ Bessel function.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs \cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
%TODO examples shown below?
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is generally smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

To summarize, the additional terms are which are added to model the internal pulse dynamics arising from a single TM$_{010}$-mode cylindrical RF cavity are
\begin{gather}
  M_{z}^{RF} = \left [ \frac{ e \Omega E_{0} }{ v_{\smallzero} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \\
  \begin{aligned}
  M_{\smallT}^{RF} = & e E_{0} \left [ \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \right. \\ \times & \left. \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ]
  \end{aligned}
\end{gather}
Additionally, since an RF cavity can act as a pulse accelerator (as seen in the leading term of \ref{eq:RF_Efield_approx}) an additional force term
\begin{equation}
  F_{z}^{RF} = e E_{0} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \, \text{,}
\end{equation}
should be added to the equation of motion governing the propagation of the pulse down the column.
% excluded example section from JAP paper as it will need new graphics
